Summary Tables

### 2020-02-24 summary_tables_outcomes.Rmd
Use qualified scen names

@@

      print(kable(format(td3, scientific = F), caption = paste('Who Hit Whom (WHW) ', cs, ' matrix for ', city)))
      cat("\n")

@@

      all_whw[[cs]][[city]] <- td
    }

@@

@@

fname <- paste("whw", cs)

td <- st[[cs]]

@@

    for (cs in names(io[[city]]$outcomes$whw)){
      # cs <- 'Baseline'
      # city <- 'mexico_city'
      if (length(names(io[[city]]$outcomes$whw$Baseline)) == 2){
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td3 <- left_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T))
      td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

      }else if(names(io[[city]]$outcomes$whw$Baseline) == 'whw'){
        td3 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
        td3[td3$mode == 'pedestrian', ]$mode <- 'walking'
      }else {

@@

      td4[, 2] <- round((td4[,3] / td4[,2]) * 100000, 1)

>>>>

scen_names_w_baseline <- append('baseline', scen_names)
scen_lt <- data.frame("scen_name" = names(io$accra$outcomes$whw), "val" = scen_names_w_baseline, stringsAsFactors = FALSE)

@@

      var <- scen_lt %>% filter(scen_name == cs) %>% select(val) %>% as.character()

      print(kable(format(td3, scientific = F), caption = paste('Who Hit Whom (WHW) ', var, ' matrix for ', city)))
      cat("\n")

@@

      all_whw[[var]][[city]] <- td
    }

@@

   #var <- scen_lt %>% filter(scen_name == cs) %>% select(val) %>% as.character()

   #print(var)

@@

var <- scen_lt %>% filter(scen_name == cs) %>% select(val) %>% as.character()

fname <- paste("whw_", var, ".csv")

td <- st[[var]]

@@

    for (cs in names(io[[city]]$outcomes$whw)){
      # cs <- 'Baseline'
      # city <- 'vizag'
      if (length(names(io[[city]]$outcomes$whw$Baseline)) == 2){
      td1 <- round(io[[city]]$outcomes$whw[[cs]]$nov) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td2 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
      td3 <- left_join(td2, td1, by = 'mode') %>% mutate(count = rowSums(.[2:3], na.rm = T))
      td3[td3$mode == 'pedestrian', ]$mode <- 'walking'

      }else if(length(names(io[[city]]$outcomes$whw$Baseline)) == 1 && names(io[[city]]$outcomes$whw$Baseline) == 'whw'){
        td3 <- colSums(round(io[[city]]$outcomes$whw[[cs]]$whw)) %>% as.data.frame() %>% rownames_to_column() %>% rename(mode = rowname) %>% rename_at(2, ~"count")
        td3[td3$mode == 'pedestrian', ]$mode <- 'walking'
      }else if(length(names(io[[city]]$outcomes$whw$Baseline)) == 1 && names(io[[city]]$outcomes$whw$Baseline) == 'nov'){

@@

      td4[, 2] <- round((td4[,3] / td4[,2] ) * 100000, 4)
      # / sum(io[[city]]$demographic$population, na.rm = T)
